Declarative Deployment Reconfiguration of Pulverised Collective Adaptive Systems at Runtime \thanks{ This work has been supported by the Italian PRIN Project COMMON-WEARS (2020HCWWLP) and the EU/MUR FSE REACT-EU PON R\&I 2014-2020. }

### 2023-05-21 paper-2023-acsos-pulverization.tex
Minors

In this section,
we exercise the proposed framework through two case studies.
%
In the former,
we show a small-scale demonstrator of a safety system warning people when a room capacity is exceeded
to showcase the integration of the framework with established technologies\footnote{
    \url{https://github.com/nicolasfara/ACSOS-2023-pulverization-crowd-room}
};
in the latter,
we simulate a city-scale distributed application deployed for a urban event
and show how the dynamic reconfiguration may help to balance
cost, energy consumption and \ac{qos}\footnote{
    \url{https://github.com/nicolasfara/ACSOS-2023-pulverization-evaluation}
}.
%
Both experiments were released with a permissive open-source licence and archived for future reference on
Zenodo~\cite{https://doi.org/10.5281/zenodo.7933160, https://doi.org/10.5281/zenodo.7948801}.

@@

%\subsection{Automatic/Autonomic Deployment and Reconfiguration}
%\label{sec:rw:autodep}
%
A comprehensive conceptual framework
 on automatic deployment of distributed systems
 is provided in~\cite{DBLP:journals/jss/ArcangeliBL15}.
%
A more recent survey~\cite{coullon2023swreconfig} focuses
 on formal techniques for verifying the correctness of reconfigurations
 in component-based distributed software systems.
%
Indeed, formal models can help specify reconfigurable architectures: examples include
\emph{DR-BIP}~\cite{Ballouli18dr-bip}
and \emph{DReAM}~\cite{denicola2020dream-dynamic-reconfig-arch-modelling}.
%
Both are based on the same conceptual model: they 
 feature \emph{components} (capturing behaviour),
\emph{connectors} (capturing the interaction between components' \emph{ports}),
\emph{maps} (logical topologies),
and \emph{deployments} (associating components to map locations),
overall organised in \emph{motifs} (dynamic architectural configurations),
to model and analyse dynamic architectures.
%
%\meta{TODO: say something about our positioning wrt verification of reconfigurations}

>>>>

In this section,
we exercise the proposed framework through two case studies.
%
In the former,
we show a small-scale demonstrator of a safety system warning people when a room capacity is exceeded, 
to showcase the integration of the framework with established technologies\footnote{
    \url{https://github.com/nicolasfara/ACSOS-2023-pulverization-crowd-room}
};
in the latter,
we simulate a city-scale distributed application deployed for a urban event
and show how the dynamic reconfiguration may help to balance
cost, energy consumption, and \ac{qos}\footnote{
    \url{https://github.com/nicolasfara/ACSOS-2023-pulverization-evaluation}
}.
%
Both experiments were released with a permissive open-source licence and archived for future reference on
Zenodo~\cite{https://doi.org/10.5281/zenodo.7933160, https://doi.org/10.5281/zenodo.7948801}.

@@

%\subsection{Automatic/Autonomic Deployment and Reconfiguration}
%\label{sec:rw:autodep}
%
A comprehensive conceptual framework
 on automatic deployment of distributed systems
 is provided in~\cite{DBLP:journals/jss/ArcangeliBL15}.
%
A more recent survey~\cite{coullon2023swreconfig} focuses
 on formal techniques for verifying the correctness of reconfigurations
 in component-based distributed software systems.
%
Indeed, formal models can help specify reconfigurable architectures: examples include
\emph{DR-BIP}~\cite{Ballouli18dr-bip}
and \emph{DReAM}~\cite{denicola2020dream-dynamic-reconfig-arch-modelling}.
%
Both are based on the same conceptual model: they 
 feature \emph{components} (capturing behaviour),
\emph{connectors} (capturing the interaction between components' \emph{ports}),
\emph{maps} (logical topologies),
and \emph{deployments} (associating components to map locations),
overall organised in \emph{motifs} (dynamic architectural configurations),
to model and analyse dynamic architectures.
%
These tools can support \emph{reasoning} about reconfigurations and \emph{verification}.

%\meta{TODO: say something about our positioning wrt verification of reconfigurations}
